\documentclass[a4paper,12pt]{article}
\begin{document}

\section{Project description}

\subsection{Introduction}
The Traffic Simulation System can simulate various kinds of vehicles that are running on a complicated road network. The road network contains multi-lane roads, intersections and roundabouts. The user can manage the simulation by adding vehicles, setting traffic lights on chosen intersections, changing time step, and so on. The real-time situation of the traffic will help user to compare and find out which traffic plan works better.

\subsection{Features of the system}
FE-1: The Traffic Simulation System should simulate different kinds of vehicles, including cars, buses and ambulances.\\
FE-2: The Traffic Simulation System should build a road network which contains multi-lane roads, intersections and roundabouts.\\
FE-3: The Traffic Simulation System should have traffic lights and allow the user to manage relevant policy to control the traffic.\\
FE-4: The Traffic Simulation System should allow the user to define where the vehicles enter and leave the road network.\\
FE-5: The Traffic Simulation System should allow the user to add arbitrary quantity and different kinds of vehicles into the road network at any time.\\
FE-6: The Traffic Simulation System should allow the user to decide the behaviors of drivers of cars, which includes reckless behavior, cautious behavior and normal behavior.\\
FE-7: The Traffic Simulation System should present real time situation of the traffic.\\
FE-8: The Traffic Simulation System should allow the user to control the simulation.


\subsection{Use case}
UC-1: Add vehicles: car, bus, ambulance\\
UC-2: Set traffic lights\\
UC-3: Define entry/exit point\\
UC-4: Define driver's behavior\\
UC-5: Check real-time traffic situation\\
UC-6: Control simulation

\subsection{Extent of version}
\begin{table}[!htbp]
\centering
\begin{tabular}{|p{1.2cm}|p{3.8cm}|p{4.5cm}|p{3cm}|}
\hline
Feature & Version1 & Version2  & Version3\\
\hline
FE-1& One type of vehicle, car which only stops when the traffic light turns red. & Tow types of vehicle, car and bus. Bus can break shortly at the bus stop. & Three types of vehicles, car, bus and ambulance.\\
\hline
FE-2& One road which has no passing lane, and one intersection. & Multi-lane roads with intersections. & Roundabouts.\\
\hline
FE-3& One traffic light and the simple policy. & Many traffic lights and it allows the,user to set traffic light in junction. & User can choose the main road.\\
\hline
FE-4& Single entry point and exit point. & Random entry points and exit points. & Entry points and exit points are defined by user.\\
\hline
FE-5& The system has specific number of cars. & User can add arbitrary quantity of cars,and buses. & User can add ambulances into the system.\\
\hline
FE-6& Default all behaviors as normal. & User can choose drivers' behaviors from three types: reckless behavior, cautious behavior and normal behavior. & Done.\\
\hline
FE-7& Present the color of traffic lights. & Display the average speed of all vehicles in the simulation, number of different vehicles, different behaviors of the drivers. & Done.\\
\hline
FE-8& The system is controlled by itself. & User can control the simulation by changing time step and changing time for switching lights. & User can control the system by changing the speed.\\
\hline
\end{tabular}
\end{table}



\section{Project organisation}
\subsection{Tools}
As specified in the requirements, we use:
\begin{itemize}
    \item{Git and GitHub - for version control and repository management}
    \item{\LaTeX - for creating documentation}
\end{itemize}

For drawing diagrams for the documentation, we use Gliffy.

We have chosen Java 8 as the language to implement our project with. To make building of the project and dependency management as simple as possible, we employ Apache Maven. This in turn enables to use Travis Continuous Integration - a free service that checks if every commit pushed to the repository builds and if the tests run.

For testing, we use the JUnit library.

For distributing tasks and controlling progress, we use GitHub Issues.

\subsection{Process}
We use a Scrum-like method to manage out project. There are week-long iterations, which start with a meeting every Thursday. During the meeting, we establish the goals to achieve in the iteration and every team member is assigned tasks to complete within the timeframe of the iteration. If any tasks are leftover from the previous iteration, they are also reassigned.

We maintain three levels of branches in the Git repository:
\begin{itemize}
    \item{\emph{master} - branch for working code which integrates and is usable. We make a \emph{master} snapshot by merging changes from \emph{dev} at the end of every iteration. All code has to build and pass its tests on Travis.}
    \item{\emph{dev} - the development branch. Here, the team members merge their new features and work on integrating them together. All code has to build and pass its tests on Travis.}
    \item{Feature branches - active development branches. Normally, there is one branch per task belonging to one team member. They are merged into dev when the task is finished (or when the task achieved a stable, partially completed state).}
\end{itemize}

When a team member starts working on task, they create a new feature branch with the name specified in the task. The names are all prefixed with \emph{feat-}. 

When the work is done, they submit a pull request closing the task. At this point, another team member reviews the code, checking the Travis build and tests status and potentially making suggestions about improvements. This is to ensure consistency in the code and that each piece of the codebase is known by at least two members.

If the reviewer and the submitter are both satisfied with the state of the pull request, the reviewer closes the pull request and the task by merging the changes into \emph{dev}. If the reviewer and the submitter cannot reach an agreement on some issue, they ask for help from a third person, a mediator. In extreme cases, the issue is resulted by team-wide vote.

\subsection{Schedule}
\begin{table}[!htbp]
    \centering
    \caption{Schedule}
    \label{schedule}
    \begin{tabular}{|l|l|}
        \hline
        04.02 - 10.02 & Something \\ \hline
        11.02 - 17.02 & Something \\ \hline
        18.02 - 24.02 & Something \\ \hline
        25.02 - 03.03 & Something \\ \hline
        04.03 - 10.03 & Something \\ \hline
        11.03 - 17.03 & Something \\ \hline
        18.03 - 24.03 & Something \\ \hline
        25.03 - 31.03 & Something \\ \hline
    \end{tabular}
\end{table}

\subsection{Peer assessment}
There are two peer assessment rounds, one for the first half of the project (3rd March) and one for the second (31st March).

On each round, each team member anonymously allocates 100 points to team members on their ballot, based how big they think their contributions were. The ballots are then shuffled. The ballots are used to reach an agreement about what the point distribution should be. If an agreement is not reached, an average of the distributions is taken and the result is scaled up so it sums to 100 again.

After the second round, the team members discuss what should be the final distribution based on the two distributions from two halves of the project. If an agreement is not reached, the averaging procedure described above is used.


\end{document}
